---
title: "Final Project"
author: "Jiayi Ge, Yue Liu, Songqi Wang, Kexin Zhang, TUT 0112, L1"
subtitle: Analysis of Internet Use in the World
output:
  beamer_presentation: default
  ioslides_presentation: default
  widescreen: yes
---


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
library(rpart)
library(partykit)
library(knitr)
library(dplyr) 
select <- dplyr::select
path <- "https://raw.githubusercontent.com/ntaback/UofT_STA130/master/Fall2018/Finalproject/"

democracyindex2017 <- read_csv(paste0(path,"democracyindex2017.csv"))
education_cia2017 <- read_csv(paste0(path,"education_cia2017.csv"))
gdpppp_cia2017 <- read_csv(paste0(path,"gdpppp_cia2017.csv"))
lifeexpect_cia2017 <- read_csv(paste0(path,"lifeexpect_cia2017.csv"))
healthexpend_cia2017 <- read_csv(paste0(path,"healthexpend_cia2017.csv"))
internetusers_cia2017 <- read_csv(paste0(path,"internetusers_cia2017.csv"))
telephonelines_cia2017 <- read_csv(paste0(path,"telephonelines_cia2017.csv"))
population_cia2017 <- read_csv(paste0(path,"population_cia2017.csv"))
world_regions <- read_csv(paste0(path,"world_regions.csv"))
```

## Introduction
- The Internet usage is an essential intermedia in globalization and modern society.
- The Internet usage is different around the world.
- How different are the Internet usage in different countries?
- What are the factors that have impact on Internet usage?

## Objectives
- How can we define internet use in a country?
- Do different regions of the world have different internet usage? 
- According to our definition of internet use, what is the impact of democracy, education, economy, and health on internet use? 

## Data
- Internet Usage = Internet Users/Population


- Democracy Score
- Education Expenditures 
- GDP per capita
- Life Expectancy
- World Region

## Data Cleaning

- Select the columns and combine them into one dataframe with proper names
- Change some character data, like GDP with $ sign, into type of double
- Correct one spelling mistake in the data of region 
- In some small countries, more users than population. The IntUsage >1 are removed.

## Data Summary
```{r, echo = FALSE,warning=FALSE}
Democracy = democracyindex2017 %>% filter(Score != 'Score')
Democracy = Democracy %>% mutate(DemocracyScore = as.numeric(as.character(Democracy$Score)))
Democracy = Democracy %>% mutate(Government_type = Category)
Democracy = Democracy %>% select(Country, Government_type, DemocracyScore)

Education = education_cia2017 %>% mutate(Country = education_cia2017$Country, Education_GDP = education_cia2017$'(% OF GDP)')
Education = Education %>% select(Country, Education_GDP)

GDP_PPP = gdpppp_cia2017 %>% mutate(GDP_Per_Capita = as.numeric(gsub("[$,]","",as.character(gdpppp_cia2017$`GDP - PER CAPITA (PPP)`))))
GDP_PPP = GDP_PPP %>% select(Country, GDP_Per_Capita)

Life_expectancy = lifeexpect_cia2017 %>% mutate(Lifetime = lifeexpect_cia2017$`(YEARS)`)
Life_expectancy = Life_expectancy %>% select(Country, Lifetime)

Health = healthexpend_cia2017 %>% mutate(Healthexpend = healthexpend_cia2017$`(% OF GDP)`)
Health = Health %>% select(Country, Healthexpend)

Internetusers = internetusers_cia2017 %>% mutate(IntUsers = internetusers_cia2017$`INTERNET USERS`)
Internetusers = Internetusers %>% select(Country, IntUsers)

TeleLines = telephonelines_cia2017 %>% mutate(TeleLines = telephonelines_cia2017$`TELEPHONES - MAIN LINES IN USE`)
TeleLines = TeleLines %>% select(Country, TeleLines)

Population = population_cia2017 %>% mutate(Population = population_cia2017$POPULATION)
Population = Population %>% select(Country, Population)

Regions = world_regions %>% select(Country, Region)
Regions[212,2] = 'Asia & Pacific'

Tidy_Data = Democracy %>%
  full_join(Education, by = "Country") %>%
  full_join(GDP_PPP, by = "Country") %>%
  full_join(Life_expectancy, by = "Country") %>%
  full_join(Health, by = "Country") %>%
  full_join(Internetusers, by = "Country") %>%
  full_join(TeleLines, by = "Country") %>%
  full_join(Population, by = "Country") %>%
  full_join(Regions, by = "Country")

Tidy_Data = Tidy_Data %>% mutate(IntUsage = IntUsers/Population)
Tidy_Data = Tidy_Data %>% arrange(Country) %>%
  filter(IntUsage <= 1)
Tidy_Data = Tidy_Data[c(1,12,2,3,4,5,6,7,8,9,10,11)]
glimpse(Tidy_Data)

```

## Statistic method 1:Boxplot

- We create boxplot by using geom_boxplot() fuction in R language which belongs to library(ggplot2) package to describe the relationship between the 
Region and IntUsage. 

- We create boxplot by using geom_boxplot() fuction in R language which belongs to library(ggplot2) package to describe the relationship between the Government_type and IntUsage.

## Statistic method 2: linear regression

- We create the linear regression by using lm() fuction to describe the relationship between IntUsage and Region. 

- We create the linear regression by using lm() fuction to describe the relationship between IntUsage and DemocracyScore.

- We create the linear regression by using lm() fuction to describe the relationship between IntUsage and Education_GDP.

- We create the linear regression by using lm() fuction to describe the relationship between IntUsage and GDP_Per_Capita.

- We create the linear regression by using lm() fuction to describe the relationship between IntUsage and Lifetime.

## Region
```{r,echo=FALSE, warning = FALSE}
compare_Reg_usage = compare_Reg_usage = Tidy_Data %>% select(Country, IntUsage, Region)
compare_Reg_usage = compare_Reg_usage %>% filter(!is.na(IntUsage))
compare_Reg_usage = compare_Reg_usage %>% filter(!is.na(Region))

ggplot(data = compare_Reg_usage, aes(x = Region,  y = IntUsage, color = Region)) + geom_boxplot(outlier.shape = NA)+geom_jitter(position = position_jitter(width=.1, height=0)) + scale_x_discrete(limits=c("Africa","Asia & Pacific", "Arab States","South/Latin America", "Europe", "North America")) + theme(axis.text.x  = element_text(angle=0, vjust=0.5, size=7)) + labs(title="Region vs IntUsage") +
  theme(plot.title=element_text(size=15, 
                                    face="bold", 
                                    family="American Typewriter",
                                    hjust=0.5,
                                    lineheight=1.2))
```


## Region
```{r,echo=FALSE,, warning = FALSE}
compare_Reg_usage$Region <-factor(compare_Reg_usage$Region)
compare_Reg_usage<-within(compare_Reg_usage,Region<- relevel(Region, ref = "Asia & Pacific"))
signif(summary(lm(IntUsage ~ Region, data = compare_Reg_usage))$coefficient,digits = 4)
```

## Democracy
```{r, echo = FALSE, warning = FALSE}
compare_Dem_usage = Tidy_Data %>% select(Country, IntUsage, DemocracyScore)
compare_Dem_usage = compare_Dem_usage %>% filter(!is.na(IntUsage))
compare_Dem_usage = compare_Dem_usage %>% filter(!is.na(DemocracyScore))

ggplot(data = compare_Dem_usage, aes(x = DemocracyScore,  y = IntUsage)) + geom_point() + geom_smooth(method="lm") + theme_bw() +
  labs(title="Democracy score vs IntUsage", x="Democracy score")+
  theme(plot.title=element_text(size=15, 
                                    face="bold", 
                                    family="American Typewriter",
                                    hjust=0.5,
                                    lineheight=1.2))
```

## Democracy
```{r, echo = FALSE,warning = FALSE}
summary(lm(IntUsage ~ DemocracyScore, data = compare_Dem_usage))
```

## Democracy
```{r,echo=FALSE,warning = FALSE}

compare_Cat_usage = compare_Cat_usage = Tidy_Data %>% select(Country, IntUsage, Government_type)
compare_Cat_usage = compare_Cat_usage %>% filter(!is.na(IntUsage))
compare_Cat_usage = compare_Cat_usage %>% filter(!is.na(Government_type))

ggplot(data = compare_Cat_usage, aes(x = Government_type,  y = IntUsage)) + geom_boxplot() + labs(title="Government type vs IntUsage", x="Government type") +
  theme(plot.title=element_text(size=15, 
                                    face="bold", 
                                    family="American Typewriter",
                                    hjust=0.5,
                                    lineheight=1.2))

```

## Education
```{r,echo = FALSE,warning = FALSE}
compare_edu_usage = Tidy_Data %>% select(Country, Education_GDP, IntUsage)
compare_edu_usage = compare_edu_usage %>% filter(!is.na(IntUsage))
compare_edu_usage = compare_edu_usage %>% filter(!is.na(Education_GDP))

ggplot(data = compare_edu_usage, aes(x = Education_GDP,  y = IntUsage)) + geom_point() + geom_smooth(method="lm") + theme_bw() +
  labs(title="Education % of GDP vs IntUsage", x="Education % of GDP") +
  theme(plot.title=element_text(size=15, 
                                    face="bold", 
                                    family="American Typewriter",
                                    hjust=0.5,
                                    lineheight=1.2))

```

## Education
```{r, echo = FALSE,warning = FALSE}
summary(lm(IntUsage ~ Education_GDP, data = compare_edu_usage))
```

## Economy
```{r,echo = FALSE,warning = FALSE}
compare_gdp_usage = Tidy_Data %>% select(Country, GDP_Per_Capita, IntUsage)
compare_gdp_usage = compare_gdp_usage %>% filter(!is.na(GDP_Per_Capita))
compare_gdp_usage = compare_gdp_usage %>% filter(!is.na(IntUsage))

ggplot(data = compare_gdp_usage, aes(x = GDP_Per_Capita,  y = IntUsage)) + geom_point() + geom_smooth(method="lm") + theme_bw() +
  labs(title="GDP per capita vs IntUsage", x="GDP per capita") +
  theme(plot.title=element_text(size=15, 
                                    face="bold", 
                                    family="American Typewriter",
                                    hjust=0.5,
                                    lineheight=1.2))

```

## Economy
```{r, echo = FALSE,warning = FALSE}
summary(lm(IntUsage ~ GDP_Per_Capita, data = compare_gdp_usage))
```

## Health
```{r,echo = FALSE,warning = FALSE}
compare_life_usage = Tidy_Data %>% select(Country, Lifetime, IntUsage)
compare_life_usage = compare_life_usage %>% filter(!is.na(Lifetime))
compare_life_usage = compare_life_usage %>% filter(!is.na(IntUsage))

ggplot(data = compare_life_usage, aes(x = Lifetime,  y = IntUsage)) + geom_point() + geom_smooth(method="lm") + theme_bw() +
  labs(title="Life Expectancy vs IntUsage", x="Life Expectancy") +
  theme(plot.title=element_text(size=15, 
                                    face="bold", 
                                    family="American Typewriter",
                                    hjust=0.5,
                                    lineheight=1.2))

```

## Health
```{r, echo = FALSE,warning = FALSE}
summary(lm(IntUsage ~ Lifetime, data = compare_life_usage))
```

## Final Model
```{r, echo = FALSE,warning = FALSE}

kable(format(summary(lm(IntUsage ~ DemocracyScore+GDP_Per_Capita+Lifetime+Education_GDP,data = Tidy_Data))$coefficient),scientific = TRUE)
```

R-squared:
```{r,echo = FALSE,warning = FALSE}
summary(lm(IntUsage ~ DemocracyScore+GDP_Per_Capita+Lifetime+Education_GDP,data = Tidy_Data))$r.sq
```

## Conclusion
- We do have a difference between the internet usages of different countries. Generally, developed countries or developed regions have a higher Internet usage.
- Economy and health have a strong positive impact on internet usage.
- Democracy level have a week positive impact on internet usage.
- Education has no impact on internet usage.

## Acknowledgment
We are thankful to our Prof.Taback for his knowledge that provided to us during the course of this seminar and his presentation.

Especially thanks to our TA, Yang Zhu for his valuable guidance and encouragement.

Last but not least, we would also want to extend our appreciation to those could not be mentioned here due to the limitation of time.